### 2013-06-13 analytical_approximation/analytic.tex
more

>>>>

Since $R(q)$ is invertible, we get (?)

$$
p_R(r) = \frac{N\lambda}{2^{\frac{N}{2} + 1}} \left(\frac{\lambda}{r^2} -\lambda + \frac{1}{2} \right)^{-\frac{N}{2} - 1} 
$$

$\lambda$ was really assumed to be one from the beginning (it was the unit-ball), so

$$
p(r) = \frac{N}{2^{\frac{N}{2} + 1}} \left(\frac{1}{r^2} - \frac{1}{2} \right)^{-\frac{N}{2} - 1}
$$

Next step: What if it's \emph{not} a unit-ball? Then we'll get $p(r)$ as a function of the ball's radius. We dealt with the $\lambda$ separately, but there is also a term from the $\chi^2$ distributions (which should be $\lambda^2$ that I didn't carry through).
